Security Audit of Safeplug

### 2014-01-14 intro.tex
edited captions

\section{Introduction}
\label{sec:intro}
    -Motivation
    -Tor
    -Safeplug
Safeplug is a product that launched last week from the cloud storage company Pogoplug, offering to let users browse the web with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.  Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user’s router and the internet \cite{wired}.  Pogoplug’s marketing pitch centers around the protection of user’s IP addresses by using Tor \cite{safeplug,bittech}.  Lots of folks are excited about the idea, but waiting to see a security audit, including Bruce Schneier \cite{schneier}.  Gigaom quotes Pogoplug CEO Dan Putterman as saying the box uses “vetted software” \cite{gigaom} but who knows what that means?

>>>>

\section{Introduction}
\label{sec:intro}

User privacy is becoming increasingly important as more Internet users realize how vulnerable they are to attackers and eavesdroppers.  This has been exacerbated by the current news about the NSA's surveillance of the Internet~\cite{nsa}.  Unfortunately, the average Internet user is not aware of how to protect themselves against malicious users.

{\bf Tor.} Among the more computer-savvy Internet users, Tor is gaining popularity for this reason.  Tor is a service that provides anonymous communication as an onion router; it also makes a tradeoff between anonymity, usability, and efficiency~\cite{tor}.  While Tor provides some measure of anonymity, the average Internet user does not know about it or how it works.

{\bf Safeplug.} Safeplug is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor without having to know about it or how it works.  It allows users to browse the web with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.  Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user’s router and the internet \cite{wired}.  Pogoplug’s marketing pitch centers around the protection of user’s IP addresses by using Tor \cite{safeplug,bittech}.

### 2014-01-14 results.tex
edited captions

\begin{figure}[th]
\begin{center}
\includegraphics[width=\textwidth]{funnydesc.png}
\caption{This is a figure.}
\label{fig:funnydesc}
\end{center}
\end{figure}

\begin{figure}[th]
\begin{center}
\includegraphics[width=\textwidth]{relaydesc.png}
\caption{This is a figure.}
\label{fig:relaydesc}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.75\textwidth]{instructions}
\caption{This is a figure.}
\label{fig:instructions}
\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=.75\textwidth]{proxyconfig}
\caption{This is a figure.}
\label{fig:proxyconfig}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.75\textwidth]{settings}
\caption{This is a figure.}
\label{fig:settings}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\centering
\begin{subfigure}[b]{.4\textwidth}
\includegraphics[width=\textwidth]{before}
\caption{This is a figure.}
\label{fig:before}
\end{subfigure}%
\quad
\begin{subfigure}[b]{.4\textwidth}
\includegraphics[width=\textwidth]{after}
\caption{This is a figure.}
\label{fig:after}
\end{subfigure}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.5\textwidth]{funnygoogle}
\caption{This is a figure.}
\label{fig:funnygoogle}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\centering
\begin{subfigure}[b]{.3\textwidth}
  \includegraphics[width=\textwidth]{safeplug_top}
  \caption{This is a figure.}
  \label{fig:top}
\end{subfigure}%
\qquad
\begin{subfigure}[b]{.3\textwidth}
\includegraphics[width=\textwidth]{safeplug_bottom}
\caption{This is a figure.}
\label{fig:bottom}
\end{subfigure}
\caption{Safeplug circuit board after the teardown.}
\end{figure}

>>>>

\begin{figure}[th]
\begin{center}
\includegraphics[width=\textwidth]{funnydesc.png}
\caption{Description of Tor on Safeplug settings page.}
\label{fig:funnydesc}
\end{center}
\end{figure}

\begin{figure}[th]
\begin{center}
\includegraphics[width=\textwidth]{relaydesc.png}
\caption{Description of a Tor relay on Safeplug settings page.}
\label{fig:relaydesc}
\end{center}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=.75\textwidth]{instructions}
\caption{Configuration instructions.}
\label{fig:instructions}
\end{center}
\end{figure}

\begin{figure}[t]
\begin{center}
\includegraphics[width=.75\textwidth]{proxyconfig}
\caption{Proxy Configuration.}
\label{fig:proxyconfig}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.75\textwidth]{settings}
\caption{Settings page.}
\label{fig:settings}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\centering
\begin{subfigure}[b]{.4\textwidth}
\includegraphics[width=\textwidth]{before}
\caption{Web page before using Tor and ad-blocking.}
\label{fig:before}
\end{subfigure}%
\quad
\begin{subfigure}[b]{.4\textwidth}
\includegraphics[width=\textwidth]{after}
\caption{Web page after using Tor and ad-blocking.}
\label{fig:after}
\end{subfigure}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.5\textwidth]{funnygoogle}
\caption{Google's response after trying to log in.}
\label{fig:funnygoogle}
\end{center}
\end{figure}

@@

\begin{figure}[htb]
\centering
\begin{subfigure}[b]{.3\textwidth}
  \includegraphics[width=\textwidth]{safeplug_top}
  \caption{Top of the board inside the Safeplug device.}
  \label{fig:top}
\end{subfigure}%
\qquad
\begin{subfigure}[b]{.3\textwidth}
\includegraphics[width=\textwidth]{safeplug_bottom}
\caption{Bottom of the board inside the Safeplug device.}
\label{fig:bottom}
\end{subfigure}
\caption{Safeplug circuit board after the teardown.}
\end{figure}
